Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-08-23 review/Response to reviews.Rmd

## Figures: {#R1-figs}

> Fig 2 -- This was only cited in the discussion as far as I can tell.
> Bring it back into the results?

> Fig 3A -- The results mention something about survival approaching 1 -- I wasn't sure if that was supposed to be visible here.

This was referring to a previous iteration of the figure where the y-axis was on the response scale.
We have reverted the figure to this version (see response below) and this should be obvious now.

@@

> Fig 3 -- I mentioned this earlier, but I wasn't really clear on how to interpret effect size.
> I see the explanation in L 539 in the legend, but I don't really know what that means.
> Since this is such an important result of the paper, it would help the reader if they were walked through this idea.
> What is a negative vs. positive effect size in relation to plant size (does this compare to the median size)?
> I am likely missing something here.
> (I think the challenge for me is that I kept wanting the figures to fit into a more standard demographic paper -- like the probability of survival based on size, but then I realized something different was being shown here.)

These plots were the evaluated smooths on the link scale.
We agree that they were difficult to interpret in that form, so we have added the model intercept and back-transformed them to be on their respective response scales (e.g. probability for flowering and survival).
This is equivalent to the marginal effect of log(size_t)---that is, without considering the additive effect of lagged SPEI or the random intercepts for different plots and for plants that had not flowered in the previous year (the reference level for the `flwr_prev` factor we included as a parametric covariate).
We have not clarified that in the figure caption.

### 2021-08-23 doc/paper.Rmd
go back to back-transformed marginal effects plots (#83, #95)

```{r}
size_cap <- "Smooth effect from models of plant size in the previous census on (a) survival, (b) log(size), and (c) flowering probability; these values correspond to the additive term s~1~(z~i~) in eq. 1. The bands depicting the 95% confidence interval include uncertainty in the intercept and uncertainty due to smoothness selection; the smooths for 1-ha fragments and continuous forest are fit in separate models. (d) Plant size distribution by habitat type (solid line = 1-ha fragments, dashed line = Continuous Forest)."
```

>>>>

```{r}
size_cap <- "Marginal effect of plant size in the previous census on (a) survival, (b) log(size), and (c) flowering probability. Plots a--c were created by evaluating the smooth functions of $log(size_t)$ at observed values, adding the model intercepts, and back-transforming (when appropriate) to the response scale (e.g. probability for a and c). The bands depicting the 95% confidence interval include uncertainty in the intercept and uncertainty due to smoothness selection; the smooths for 1-ha fragments and continuous forest are fit in separate models. (d) Plant size distribution by habitat type (solid line = 1-ha fragments, dashed line = Continuous Forest)."
```
